### 2024-07-05 paper/paper-papaja-revising.Rmd
resub

keywords          : "Illusory truth; Metacognition; Cognitive Psychology; Misinformation"
wordcount         : "5660"

@@

Crucially, our theory draws no connection between metacognitive experiences and reduced truth judgments for statements expressing $R$ where $P$ implies $\neg R$. Such a connection would require a cogent theory of how conceptual "disfluency" might be engendered to reduce truth judgments without the process of inference that would implicate changes in belief. Current accounts have not developed such a theory [e.g. c.f. @AlterOppenheimer2009Uniting; @VogelEtAl2020Truth], and it appears unlikely to be workable: people frequently encounter chains of statements invoking different concepts, yet they do so seemingly without issue, as considering one topic does not necessarily make it more difficult to consider another unrelated topic.

>>>>

keywords          : "Illusory truth; Metacognition; Cognitive Psychology; Misinformation"
wordcount         : "6791"

@@

Crucially, our theory draws no connection between metacognitive experiences and reduced truth judgments for statements expressing $R$ where $P$ implies $\neg R$. Such a connection would require a cogent theory of how conceptual "disfluency" might be engendered to reduce truth judgments without the process of inference that would implicate changes in belief. Current accounts have not developed such a theory [e.g. c.f. @alter.oppenheimer2009; @VogelEtAl2020Truth], and it appears unlikely to be workable: people frequently encounter chains of statements invoking different concepts, yet they do so seemingly without issue, as considering one topic does not necessarily make it more difficult to consider another unrelated topic.
